\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[%
    margin,
    line,
]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{fourier-orns}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}
\usepackage[style=iso]{datetime2}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=8.9in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Fabian Gittins --- Curriculum Vitae (as of \today)}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

% Give hyperref some metadata
\hypersetup{%
    pdftitle={Fabian Gittins — Curriculum Vitae (CV)},
    pdfauthor={Fabian Gittins},
    pdfsubject={Fabian Gittins's academic curriculum vitae (CV)},
    pdfkeywords={physics, gravity, general relativity, neutron stars,
    gravitational waves, asteroseismology}
}

% I want small caps for the section style
\def\sectionfont{\sc}

% Generate a PDF TOC
\let\oldsection\section
\def\section#1{%
    \oldsection{#1}%
    \phantomsection%
    \addcontentsline{toc}{section}{#1}%
}

% The above seems to screw up the spacing for sections that start with lists...
\newcommand{\secstartswithlist}{\leavevmode \vspace{-\baselineskip}}

\begin{document}

\newcommand{\myname}{Fabian Gittins}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \myname \vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

\input{ContactContent.tex}

\section{Citizenship}

United Kingdom

\section{Education}

\textbf{PhD, Mathematics,} University of Southampton, UK
\hfill \textbf{Sep. 2021} \\
\vspace*{-.1in}
\begin{itemize}
    \item[] Advisor: Prof Nils Andersson
    %
    \item[] Thesis title:
    \href{https://eprints.soton.ac.uk/452900/}%
    {\textit{Gravitational waves from deformed neutron stars: mountains and tides}}
\end{itemize}

\textbf{MSci, Physics,} University of Birmingham, UK
\hfill \textbf{Jul. 2017} \\
\vspace*{-.1in}
\begin{itemize}
    \item[] Grade: First class honours
    %
    \item[] Undergraduate Master's degree with focus on theoretical physics
\end{itemize}

\section{Research Experience}

\textbf{Marie Sk{\l}odowska-Curie Postdoctoral Fellow,} Utrecht University, NL
\hfill \textbf{Oct. 2024--Present} \\
\\
\textbf{Research Fellow,} University of Southampton, UK
\hfill \textbf{Oct. 2021--Sep. 2024} \\
\\
\textbf{PhD Researcher,} University of Southampton, UK
\hfill \textbf{Sep. 2017--Sep. 2024} \\
\\
\textbf{Undergraduate Researcher,} University of Birmingham, UK
\hfill \textbf{Sep. 2016--Mar. 2017} \\
\\
\textbf{Undergraduate Researcher,} University of Birmingham, UK
\hfill \textbf{Jan.--May 2016} \\
\\
\textbf{Undergraduate Research Intern,} University of Birmingham, UK
\hfill \textbf{Jun.--Sep. 2015} \\

% Added to improve page breaks
\vspace{-1em}

\section{Research Interests}

Relativistic astrophysics, gravitational-wave astronomy and the extreme physics
of neutron stars.
One major theme is building predictive, physically faithful neutron-star models
with realistic microphysics and dynamics.
A second major theme is using gravitational waves to extract this physics and
constrain dense nuclear matter.
Currently, I advance gravitational-wave asteroseismology to probe dense-matter
physics through the modelling and detection of neutron-star oscillation modes.

\section{Grants and Awards}

\textbf{Marie Sk{\l}odowska-Curie Postdoctoral Fellowship,} European Union
\hfill \textbf{Oct. 2024--Sep. 2026}\vspace*{.05in}
\begin{itemize}
    \item[] Project lead of
    \href{https://doi.org/10.3030/101151301}{\textit{DynTideEOS}}; €203,464
\end{itemize}
\textbf{Gravitational Physics Thesis Prize,} Institute of Physics, UK
\hfill \textbf{2021} \\
\\
\textbf{Best Publication in Gravitational Physics,}
University of Southampton, UK
\hfill \textbf{2021} \\
\\
\textbf{Physics Scholarship,} University of Birmingham, UK
\hfill \textbf{2013} \\

\newpage

\input{TalksContent.tex}

% Added to improve page breaks
%\vspace{-1em}

\section{Teaching Experience}

\textbf{Instructor,} University of Southampton, UK
\vspace*{.05in}
\begin{itemize}
    \item[] MATH1007/1009, Mathematical Methods for Physical Scientists
\hfill \textbf{Feb.--May 2024}
\end{itemize}
%\newpage{}
\textbf{Guest Lecturer,} University of Southampton, UK
\vspace*{.05in}
\begin{itemize}
    \item[] MATH3072, Advanced Fluid Dynamics
\hfill \textbf{Oct. 2022, Oct. 2023}
    \item[] MATH3006, Relativity, Black Holes and Cosmology
\hfill \textbf{Apr. 2022}
\end{itemize}
\textbf{Teaching Assistant,} University of Southampton, UK
\hfill \textbf{Oct. 2017--May 2021}
\begin{itemize}
    \item[] MATH1054/1055, Mathematics for Engineering and the Environment
    %
    \item[] MATH1057, Dynamics and Relativity
    %
    \item[] MATH1058, Operational Research I and Mathematical Computing
    %
    \item[] MATH2045, Vector Calculus and Complex Variable Theory
    %
    \item[] MATH3018, Numerical Methods
    %
    \item[] MATH3087, Maths and Your Future
\end{itemize}
\textbf{Teaching Assistant,} King Edward's School, Birmingham, UK
\hfill \textbf{Jan.--Apr. 2016}
\vspace*{.05in}
\begin{itemize}
    \item[] Physics (11--16 yr)
\end{itemize}

\section{Mentoring and Supervision}

\textbf{PhD student mentoring}
\begin{itemize}
    \item[] Thibeau Wouters, Utrecht University, NL
    \hfill \textbf{Oct. 2024--Present}
    %
    \item[] Rahime Matur, University of Southampton, UK
    \hfill \textbf{Jan. 2023--Sep. 2024}
    %
    \item[] Rhys Counsell, University of Southampton, UK
    \hfill \textbf{Sep. 2021--Sep. 2024}
    %
    \item[] Shanshan Yin, University of Southampton, UK
    \hfill \textbf{Sep. 2021--Sep. 2024}
    %
    \item[] Thomas Celora, University of Southampton, UK
    \hfill \textbf{Sep. 2021--Sep. 2023}
    %
    \begin{itemize}
        \vspace{-.05in}
        \item[] Now postdoc at Institute of Space Sciences, Barcelona, ES
    \end{itemize}
\end{itemize}
\textbf{Master's student supervision}
\begin{itemize}
    \item[] Tobie Walraven, Utrecht University, NL
    \hfill \textbf{Sep. 2025--Present}
\end{itemize}

%
%\newpage{}

\section{Professional Activities, Outreach and Service}

\textbf{Virgo Collaboration, Member} \hfill \textbf{Oct. 2024--Present} \\
\textbf{Cosmic Explorer Consortium, Member} \hfill \textbf{May 2024--Present} \\
\textbf{Einstein Telescope Collaboration, Member}
\hfill \textbf{Sep. 2023--Present}

\textbf{International Astronomical Union, Junior member}
\hfill \textbf{May 2023--Present} \\
\textbf{European Astronomical Society, Member}
\hfill \textbf{Nov. 2024--Present} \\
\textbf{Royal Astronomical Society, Elected fellow}
\hfill \textbf{Jul. 2021--Present} \\
\textbf{International Society on General Relativity and Gravitation,} \\
\textbf{Lifetime member} \hfill \textbf{May 2021--Present} \\
\textbf{Institute of Physics, Member} \hfill \textbf{Apr. 2021--Present}
\begin{itemize}
    \item[] Gravitational Physics Group, Committee member
    \hfill \textbf{Oct. 2021--Sep. 2025}
\end{itemize}

\textbf{Conference organiser}
\vspace*{.05in}
\begin{itemize}
    \item[]
    \href{https://sites.google.com/view/spins-uk-2024}{SPINS-UK 2024 meeting},
    University of Southampton
    \hfill \textbf{10--12 Sep. 2024} \\
    \hspace*{1em} Local organising committee, $\sim 40$ participants
    %
    \item[]
    \href{https://plan.events.mpg.de/event/133}%
    {Continuous gravitational waves and neutron stars workshop}, \\
    Albert Einstein Institute, Hannover, DE \hfill \textbf{17--20 Jun. 2024}\\
    \hspace*{1em} Scientific organising committee, $\sim 50$ participants
    %
    \item[]
    \href{https://iop.eventsair.com/gpm2024/}%
    {Gravitational Physics Annual Meeting},
    Institute of Physics, UK \hfill \textbf{18 Jan. 2024} \\
    \hspace*{1em} Scientific organising committee, $\sim 50$ participants
    %
    \item[]
    \href{https://sites.google.com/view/britgrav23}{23rd BritGrav Conference},
    University of Southampton, UK \hfill \textbf{13--14 Apr. 2023} \\
    \hspace*{1em} Scientific and local organising committee,
    $\sim 100$ participants
\end{itemize}

\textbf{Seminar organiser}
\vspace*{.05in}
\begin{itemize}
    \item[] Gravity Seminar, University of Southampton, UK
    \hfill \textbf{Oct. 2021--Sep. 2024}
    %
    \item[] Weekly Gravity Reading Group, University of Southampton, UK
    \hfill \textbf{Jan.--Jul. 2021}
\end{itemize}

\textbf{Journal referee}
\vspace*{.05in} \\
\hspace*{1em}
Astronomy and Astrophysics,
Classical and Quantum Gravity,
Journal of Cosmology and Astroparticle Physics,
Journal of Physics G,
Monthly Notices of the Royal Astronomical Society,
Nature Astronomy,
Physical Review D,
Physical Review Letters,
The Astrophysical Journal

\textbf{Project referee}
\vspace*{.05in}
\begin{itemize}
    \item[] Postdoctoral project, University of Namur, BE \hfill \textbf{2025}
    %
    \item[] Open Fellowship,
    Engineering and Physical Sciences Research Council, UK \hfill \textbf{2024}
\end{itemize}

\textbf{Outreach}
\vspace*{.05in}
\begin{itemize}
    \item[] Southampton Science and Engineering Festival
    \hfill \textbf{7 May 2022, 18 Mar. 2023} \\
    \hspace*{1em} Organised neutron-star exhibit for general public and
    coordinated team of 10 volunteers
    %
    \item[] Mathematical Challenge \hfill \textbf{Mar.--Apr. 2020} \\
    \hspace*{1em} Marked over 200 pupil entries
    %
    \item[] Maths and Physics Workshop \hfill \textbf{8 Nov. 2017} \\
    \hspace*{1em} Demonstrated for $\sim 100$ secondary-school pupils
\end{itemize}

\textbf{Press (selected)}
\vspace*{.05in}
\begin{itemize}
    \item[]
    \href{https://www.ntvn.nl/2025/10/sporen-van-quarkmaterie-zwaartekrachtgolven/}%
    {\textit{Sporen van quarkmaterie in zwaartekrachtgolven?}}
    \hfill \textbf{1 Oct. 2025} \\
    Nederlands Tijdschrift voor Natuurkunde
    %
    \item[]
    \href{https://www.newscientist.com/article/2343788-lightest-neutron-star-ever-found-could-contain-compressed-quarks/}%
    {\textit{Lightest neutron star ever found could contain compressed quarks}},
    New Scientist \hfill \textbf{24 Oct. 2022}
    %
    \item[]
    \href{https://www.livescience.com/millimeter-tall-neutron-star-mountains.html}%
    {\textit{Neutron star `mountains' may be blocking our view of mysterious gravitational}}
    \hfill \textbf{21 Jul. 2021} \\
    \href{https://www.livescience.com/millimeter-tall-neutron-star-mountains.html}%
    {\textit{waves}}, Live Science
    %
    \item[]
    \href{https://www.theregister.com/2021/07/21/mountain_neutron_stars/}%
    {\textit{Mountains on neutron stars are not even a millimetre tall due to extreme}}
    \hfill \textbf{21 Jul. 2021} \\
    \href{https://www.theregister.com/2021/07/21/mountain_neutron_stars/}%
    {\textit{gravity}}, The Register
    %
    \item[]
    \href{https://www.independent.co.uk/space/neutron-stars-mountains-ligo-virgo-b1886426.html}%
    {\textit{Scientists find tiny mountains on neutron stars that are a fraction of a}}
    \hfill \textbf{19 Jul. 2021} \\
    \href{https://www.independent.co.uk/space/neutron-stars-mountains-ligo-virgo-b1886426.html}%
    {\textit{millimetre tall}}, The Independent
    %
    \item[]
    \href{https://gizmodo.com/neutron-stars-have-mountains-that-are-less-than-a-milli-1847309049}%
    {\textit{Neutron Stars Have Mountains That Are Less Than a Millimeter Tall}},
    Gizmodo \hfill \textbf{18 Jul. 2021}
    %
    \item[]
    \href{https://www.newscientist.com/article/2278363-neutron-stars-are-remarkably-smooth-thanks-to-their-intense-gravity/}%
    {\textit{Neutron stars are remarkably smooth thanks to their intense gravity}},
    \hfill \textbf{24 May 2021} \\
    New Scientist
    %
    \item[]
    \href{https://astrobites.org/2018/11/16/ns_breakup/}%
    {\textit{Why don’t they just break up?}}
    Astrobites \hfill \textbf{16 Nov. 2018}
\end{itemize}

\section{Computer Skills}

Advanced in Julia, Python.
Intermediate in Bash, C++, Mathematica, MATLAB.
Intermediate in high-performance computing (HTCondor, Slurm).
Markup languages: \LaTeX, Markdown.

\textbf{Software---}%
Most contributions can be found at \url{https://github.com/fgittins}.
Member of the \textit{Bilby} development team
(\url{https://github.com/bilby-dev/bilby}).
Contributor to \textit{SciML} (\url{https://sciml.ai}),
in particular \texttt{NonlinearSolve.jl}
(\url{https://github.com/SciML/NonlinearSolve.jl}).
Author of \texttt{RealisticSeismology} Julia code
(\url{https://github.com/fgittins/RealisticSeismology}).

% Twiddle this for spacing
% \newpage

\ifx\nopubs\undefined
\input{PubsContent.tex}
\else
%
\fi

%\newpage{}

\section{References}

\vspace*{.05in}
\parbox{\textwidth}{%
\textbf{Prof Nils Andersson,} Professor of Applied Mathematics \\
School of Mathematical Sciences \\
University of Southampton, \\
University Road \\
Southampton, SO17 1BJ \\
United Kingdom \\
email: \href{mailto:n.a.andersson@soton.ac.uk}{n.a.andersson@soton.ac.uk} \\
office phone: \href{tel:+44 23 8059 4551}{+44 23 8059 4551}}
%
\par
\parbox{\textwidth}{%
\textbf{Prof Chris van den Broeck,} Professor of Physics \\
Institute of Gravitational and Subatomic Physics \\
Utrecht University \\
Princetonplein 1 \\
3584 CC Utrecht \\
The Netherlands \\
email: \href{mailto:c.f.f.vandenbroeck@uu.nl}{c.f.f.vandenbroeck@uu.nl} \\
office phone: \href{tel:+31 6 25 13 3968}{+31 6 25 13 3968}}
%
\par
\parbox{\textwidth}{%
\textbf{Dr David Tsang,} Lecturer in Physics \\
Department of Physics \\
University of Bath \\
Claverton Down \\
Bath, BA2 7AY \\
United Kingdom \\
email: \href{mailto:d.tsang@bath.ac.uk}{d.tsang@bath.ac.uk}\\
office phone: \href{tel:+44 12 2538 4539}{+44 12 2538 4539}}

\end{resume}
\end{document}

% Local Variables:
% mode: latex
% End:
